Remark on the hypothetical judgment

### 2015-08-01 paper.tex
typo

Now that we have settled upon an explanation for hypothetical judgment, let us
return to the notion of propositions and implication, and their respective
notions of ``construction''. Like ``proof'', the term ``construction'' is also
ambiguous in that it may refer to an act of constructing, and it may also denote
a concrete mathematical object.

>>>>

Now that we have settled upon an explanation for hypothetical judgment, let us
return to the notions of judgment and proposition, and their respective concepts
of ``construction''. Like ``proof'', the term ``construction'' is also ambiguous
in that it may refer to an act of constructing, and it may also denote a
concrete mathematical object.
